Frequency of dwarf and massive galaxy pairs in the IllustrisTNG cosmological simulation

### 2023-03-09 paper/pears.tex
intro and 1st sec of methods

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Methodology}\label{sec:methods}
%  Our sample data was obtained using a strict set of selection criteria, as outlined in this section.
% In Sec.~\ref{sec:methods-sims}, we provide motivation for and details of the simulations utilized in this study.
% Sec.~\ref{sec:methods-am} explains the abundance matching prescription used to associate stellar masses with the dark matter subhalos.
% Sec.~\ref{sec:methods-crit} provides a detailed outline of our selection criteria and process for picking pairs.
% Finally, Sec.~\ref{sec:methods-counts} gives an overview of the properties of our sample.

\subsection{Simulation details} \label{sec:methods-sims}
    \begin{itemize}
        \item What do we require in a sim/why using TNG hydro?
        \item Brief sim details \& and the data we use (group and merger cats)
    \end{itemize}

@@

\subsection{Pair selection}\label{sec:methods-pairs}
    \begin{itemize}
        \item what types of pairs are we looking for? 
        \item why do we pick the mass range we are looking at?
        \item how do we pick out the groups we'll use (group crit)
    \end{itemize}
    \subsubsection{Selecting primaries}
            \begin{itemize}
                \item definition of prims
                \item how we use single-halo groups. 
            \end{itemize}
    \subsubsection{Selecting companions}
            \begin{itemize}
                \item companions selected by mass ratio
                \item explain pairing method for each realization
            \end{itemize}

@@

% % Baryonic processes
% Baryonic process are known to affect the dark matter halo structure of low mass ($M_*<1\times10^9\Msun$) subhalos in simulations~\citep[see e.g.][and references therein]{Sales:2022}.
% Additionally, the shallow potential well of dwarf galaxies compared to their massive counterparts may lend themselves more easily to disruption from baryonic processes such as supernova feedback, which could change the occurance rate of low mass subhalos in hydrodynamic simulations \kc{check and see if they looked at this in the TNG100 galaxy paper}.
% To study the effect of baryonic processes on the rate and separation of pairs, we require cosmological simulations which have both dark matter only runs and to full hydrodynamics.

% % details of Illustris and Illustris TNG
% The \textit{Illustris Project} ~\citep{vogelsberger14A,nelson15} and \textit{IllustrisTNG Project}~\citep{TNG1, TNG2, TNG3, TNG4, TNG5} are a set of N-body and hydrodynamic cosmological simulations which are perfectly suited for such a study. 
% We use the dark matter only and full hydrodynamic runs of both the \ill-1 and \tng100-1 simulations to explore the connection between pairs and baryonic processes. 
% Each of these simulations follows the dynamical evolution of $1820^3$ dark matter particles from $z=127$ to $z=0$ through a periodic volume of roughly $100^3$ Mpc$^3$. 
% The \ill{} simulations follow a cosmology consistent with \textit{WMAP-9}~\citep{hinshaw2013}, while the \tng{} simulations are consistent with \textit{Planck2015}~\citep{Planck2015}.
% Specifically, we use the \textit{Illustris-1-Dark}, \textit{Illustris-1}, \textit{TNG100-1-Dark}, and \textit{TNG100-1} simulations (hereafter \illd, \illh, \tngd, and \tngh{} respectively, % see Table~\ref{table:sim} for details).

% % deets on the hydrodynamics of 
% \kc{hydrodynamics details on the difference between the two hydro simulations. also include differences between the two dark simulations, if there are any besides the cosmology. }

% % subfind, sublink, and groups and subhalos
% We utilize the group catalogs produced by the \texttt{SUBFIND} algorithm ~\citep{springel2001,dolag09}. 
% These catalogs consist of halos (or "groups"), defined using the Friends-of-Friends (FoF) algorithm~\citep{davis1985} to link nearby particles, and their associated subhalos, which are over-dense and gravitationally bound dark matter structures.
% We also use the merger trees provided by the \texttt{SUBLINK} algorithm \citep{gomez15}, which tracks subhalos between snapshots using their particle data, in order to trace the mass growth and merger histories of our subhalos.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Methodology}\label{sec:methods}
We use a run of the \tngh\ simulation to select halo pairs according to a strict set of selection criteria as outlined in this section. 
In Sec.~\ref{sec:methods-sims}, we provide motivation for and details of the simulation utilized in this study.
Sec.~\ref{sec:methods-halos} outlines the initial mass cuts used to define our full sample of primary halos about which we will search for secondary companions.
Sec.~\ref{sec:methods-am} outlines the abundance matching prescription we used to associate dark matter subhalos with stellar masses.
Sec.~\ref{sec:methods-pairs} describes the second set of selection criteria we apply to obtain the full sample of dwarf and massive pairs.
In Sec.~\ref{sec:methods-props}, we show some of the properties of our entire pair sample, including the total number of pairs and stellar mass ratios.
Finally, Sec.~\ref{sec:methods-analysis} gives an overview of our analysis methods and a description of the parameters of interest in this study.

    \subsection{Simulation details} \label{sec:methods-sims}
        % Brief description of TNG hydro and which run we use.
    The \tng\ project ~\citep{TNG1, TNG2, TNG3, TNG4, TNG5} consists of a suite of dark-matter-only $N$-body as well as full physics cosmological simulations consistent with the \textit{Planck2015} \lcdm/  cosmology~\citep{Planck2015}.
    In this study we utilize data from the main high resolution full physics run of the (110.7\Mpc)$^3$ volume simulation, \textsl{TNG100-1}, which includes dark matter and baryonic particles and follows the evolution of $1820^3$ dark matter particles from $z=127$ to $z=0$.

      % subfind, sublink, and groups and subhalos
    We utilize the group catalogs produced by the \texttt{SUBFIND} algorithm~\citep{springel2001,dolag09}. 
    These catalogs consist of halos , defined using the Friends-of-Friends (FoF) algorithm~\citep{davis1985} to link nearby particles, and their associated subhalos, which are over-dense and gravitationally bound dark matter structures compared to the background. (From here, we will refer to FoF halos as "groups" and their subhalos as )
      % We also use merger catalogs generated by XX for YY purpose. 
    We also use merger trees provided by the \texttt{SUBLINK} algorithm~\citep{RG2015}, which tracks subhalos between snapshots using their DM particle data, in order to trace subhalo mass growth and merger histories.

    The large volume of this simulation offers a large statistical sample of halos to study in a cosmological context, but is also high enough resolution ($m_{\rm DM} = 7.5\times10^6\Msun$, $m_{\rm gas} = 1.4\times10^6\Msun$) that dwarf halos ($\sim1\times10^{9-10.5}\Msun$) halos are resolved into roughly hundreds or more particles, well above the resolution limit of 32 DM particles for halos identified with \texttt{SUBFIND}, and 20 gas and star particles used to construct baryonic merger trees.

        %  this MIGHT go in a different section? am I talking about this because I want to show why we use hydro instead of dark? 
    Baryonic process are known to affect the structure and formation of dark matter halos of low mass ($M_*\lesssim 1\times10^9\Msun$) subhalos in simulations~\citep[see e.g.][and references therein]{Sales:2022}.
    Additionally, the shallow potential well of dwarf galaxies compared to their massive counterparts may lend themselves more easily to disruption from baryonic processes such as supernova feedback and reionization~\citep{}, resulting in fewer low mass halos ($\lesssim 5\times10^{10}$) in hydrodynamic simulations~\citep{vogelsberger14B}.
    % Thus, the number of primaries  we expect that our choice of simulation will result in

@@

\subsection{Pair selection}\label{sec:methods-pairs}
    \begin{itemize}
        \item what types of pairs are we looking for? 
        \item why do we pick the mass range we are looking at?
        \item how do we pick out the groups we'll use (group crit)
    \end{itemize}
    \subsubsection{Selecting primaries}
            \begin{itemize}
                \item definition of prims
                \item how we use single-halo groups. 
            \end{itemize}
    \subsubsection{Selecting companions}
            \begin{itemize}
                \item companions selected by mass ratio
                \item explain pairing method for each realization
                \item minimum separation of 15kpc so that we can be more confident about the mass associated with each halo (at smaller seps, more mass will be attributed to the central, also though why we use the stellar mass associated with the max mass isntead of the current mass) 
            \end{itemize}

@@
